\textbf{Dynamic Transition Analysis with TIMES:}\\ I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions

### 2018-01-04 doc/poster.tex
closes #6
Former-commit-id: a1f7bc708ef2cd06dcbec85e63ba10690ed615b7

\begin{column}{\onecolwid} % The first column

@@

\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solve within user defined constraints such as energy generation demand.  
\end{block}

@@

\begin{column}{\sepwid}\end{column} % Empty spacer column

@@

\end{column} % End of column 2

\begin{column}{\sepwid}\end{column} % Empty spacer column

@@

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

%=======================================================
% Double Wide Figure Column 
%=========================================================
\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\twocolwid} % The double wide figure column

        \input{model-fig}
\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

>>>>

\begin{column}{\twocolwid} % The first two columns, two cols wide
\begin{columns}[t,totalwidth=\twocolwid] % Split up the first column into two, 
\begin{column}{\onecolwid} % The first column, one col wide

@@

\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.  
\end{block}

@@

@@

\end{column} % End of column 2, top half
\end{columns}
%=======================================================
% Double Wide Figure Column 
%=========================================================
\input{model-fig}

\end{column} % End of wide column, total length

@@
